RadLib: a radiative property model library for CFD

### 2021-10-23 submissions/revision_2/manuscript.tex
revision_2 submitted; radlib code used is in submissions/revision_2

Figure~\ref{f:fds} shows results of the simulation with comparison to experimental data. Three radiation models were included: the FDS default model, and the RCSLW and WSGG models from RadLib (both using four gray gases and one clear gas).
The FDS default model uses a single gray gas with a composition and temperature dependent absorption coefficient computed from RADCAL. The calculation depends on a user-specified radiation path length variable with a default value of 0.1 m, which is used in the FM Burner validation case. Further details are provided in the FDS user guide \cite{FDS}. Figure~\ref{f:fds}a shows radial profiles of mean temperature at two vertical positions. The models produce maximum radial temperature differences at 1.5R of about 70 K (6\%) between the RCSLW and the WSGG at z=2.5D, and 50 K (6\%) at z=3.5D. 
%The differences are lower at lower points in the flame since the effect of radiation on temperature is cumulative. 
Figure~\ref{f:fds}b plots height versus radiative emission per unit length along the centerline with the spread in radiative emission around the peak values being 0.94 kW/m (8\%).
%
\begin{figure}
\begin{center}
\begin{tabular}{c c}
(a) & (b) \\
\includegraphics[width=2.5 in]{fig_fds_T_mean.pdf} &
\includegraphics[width=2.5 in]{fig_fds_rad_mean.pdf}
\end{tabular}
\caption{Radial profiles of mean temperature at two heights (a) and height versus radiative emission (b) for FDS simulations of the FM Burner validation case comparing three models to experimental data.}
\label{f:fds}
\end{center}
\end{figure}
%

@@

The computational cost of the FDS simulations, relative to the default model are 1, 1.68, and 1.71 for the default, WSGG, and RCSLW model, respectively. This indicates that the cost is dominated by the radiative solver and not the computation of the radiative properties.

>>>>

Figure~\ref{f:fds} shows results of the simulation with comparison to experimental data. Three radiation models were included: the FDS default model, and the RCSLW and WSGG models from RadLib (both using four gray gases and one clear gas). A case with no radiative model is also included.
The FDS default model uses a single gray gas with a composition and temperature dependent absorption coefficient computed from RADCAL. The calculation depends on a user-specified radiation path length variable with a default value of 0.1 m, which is used in the FM Burner validation case. Further details are provided in the FDS user guide \cite{FDS}. Figure~\ref{f:fds}a shows radial profiles of mean temperature at two vertical positions. The models produce maximum radial temperature differences at 1.5R of 86 K (7\%) at z=2.5D, and 71 K (9\%) at z=3.5D. 
%The differences are lower at lower points in the flame since the effect of radiation on temperature is cumulative. 
Figure~\ref{f:fds}b plots height versus radiative emission per unit length along the centerline with the spread in radiative emission around the peak values being 1.4 kW/m (10\%).
%
\begin{figure}
\begin{center}
\begin{tabular}{c c}
(a) & (b) \\
\includegraphics[width=2.5 in]{fig_fds_T_mean.pdf} &
\includegraphics[width=2.5 in]{fig_fds_rad_mean.pdf}
\end{tabular}
\caption{Radial profiles of mean temperature at two heights (a) and height versus radiative emission (b) for FDS simulations of the FM Burner validation case comparing three models to experimental data.}
\label{f:fds}
\end{center}
\end{figure}
%

@@

The computational costs of the FDS simulations, relative to the case with no radiation are 1, 1.04, 1.62, and 2.18 for the no radiation, default, WSGG, and RCSLW model, respectively. 
%This indicates that the cost is dominated by the radiative solver and not the computation of the radiative properties.
